\subsection{Interviews}
A number of interviews were held with staff at the school. Two form tutors were interviewed, in order to gain an insight into how they believe form times could be improved through the use of interactive quizzes, and to get an idea of how they would like such a system to work. Additionally, Nick Bucknall, a head of year at the school, was interviewed; he was chosen in order to gain information on what results the system should calculate, and how best to integrate such a system within the school. He was also chosen to get a further idea of the faults with the current system. Full transcripts for each of the interviews are included below. In addition to the formal interviews held with teaching staff, a more informa meetings were held with another key members of the school community - Tim Alexander, one of the IT technicians in charge of the school's network.Due to the length of this meeting and the unwillingness of the participant to be recorded, full transcripts are not available. Instead, notes on the key topics covered have been listed in the appropriate subsection.

\subsubsection{Bryan Warr}
\input{./tex/analysis/current_system/interviews/bryan_warr.tex}

\subsubsection{Wendy Blower}
\input{./tex/analysis/current_system/interviews/wendy_blower.tex}

\subsubsection{Nick Bucknall}
\input{./tex/analysis/current_system/interviews/nick_bucknall.tex}

\subsubsection{Tim Alexander}
\input{./tex/analysis/current_system/interviews/tim_alexander.tex}

\subsubsection{Summary}
The above interviews were invaluable in solidifying the scope and features of the system. The interview with Bryan Warr gave information about the praticality of the system, and how it could best be integrated into the school day. Warr's reaction to the general idea of the application was positive, indicating that, as an idea, it could work very nicely. This was reinforced during a seperate visit to the school; upon a chance encounter with him in the corridor, he stated that he had mentioned the idea to another teacher, and they had also very much liked it. In particular, vital knowledge was gained about the horiziontal restructuring of the form system, allowing vital changes to the idea to be made.

The interview with Wendy Blower proved helpful in understanding how form tutors and their students would react to the system. She provided helpful advice about the extent to which teachers would want to be involved, and, via Beth, provided invaluble access to a real student. Additionally, she helped to clarify whether or not the system would work more effectively via an iPad or other tablet, guiding the direction of the project. She also helped in choosing whether or not teachers should have free reign over which questions should be added, or if this should be left down to house captains.

The interview with Bucknall proved the most helpful out of all interviews. He helped solidfiy the idea that the system should work on a timer that cannot be stopeed by anyone - questions should just keep moving, no matter how many people are connected to the quiz, in order that the more rebellious teachers cannot try to stop the quiz. His reaction to the live aspect were also deeply positive, and he helped come up with some initial design thoughts around this area.
