\subsection{Questionnaires}

An online questionnaire was created for students of the school to fill in, detailing their opinion on form times, how it could be improved through the use of quizzes.

\subsubsection{Questions}
The following questions were included	 on the questionnaire, distributed to students at the school:

\noindent\fbox{%
    \parbox{\textwidth}{%
        \begin{enumerate}[leftmargin=0cm,itemindent=.5cm,labelwidth=\itemindent,labelsep=0cm,align=left]
					\item How satisfied are you with your current form time experience? 1 2 3 4\\
					\item ``My form times are always well structured.'' How far do you agree or disagree with this statement? 1 2 3 4 5\\
					\item Out of the following activities you selected, which do you enjoy the most?
								\begin{itemize}
									\item Silent reading
									\item Knowledge quiz
									\item Group discussion
									\item Board games
									\item Physical activities
									\item Other\\
								\end{itemize}
					\item Approximately how often do quizzes feature in your form times? 1 2 3 4\\
					\item ``My form times would be improved if we did quizzes more often.'' How far do you agree or disagree with this statement? 1 2 3 4\\
					\item ``I find that quizzes improve the relationship between me and the rest of my form'' How far do you agree or disagree with this statement? 1 2 3 4\\
					\item Which topics have you been given quizzes on? Select all that apply.
								\begin{itemize}
									\item General knowledge
									\item Media
									\item Sports
									\item History
									\item Literature
									\item Relationships
									\item Brainteasers
									\item Other\\
								\end{itemize}
					\item To what extent do you interact with other forms in your year during form time? 1 2 3 4\\
					\item Do you believe form times would be improved by interaction with other forms? Yes No\\
					\item If you wish, please expand on your answer to the previous question.
				\end{enumerate}
    }%
}

\subsubsection{Results}
The following results were collected after the quiz had been live for 10 days. They were automatically generated using the 