\clearpage
\section{Program Variables}
This section displays the variables used in throughout the program. Due to the functional nature of the language used, variables are used freely, so their usage is rather extensive. There are two types of variables used:

\begin{itemize}
  \item Block scoped - these variables, defined using the \textit{let} keyword, are similar to standard variables used in most programming languages, and have been used for values that are in some way dynamic or likely to mutate throughout program execution.
  \item Constants - declared using the \textit{const} keyword, these variables are used for things like modules that have been imported from elsewhere in the codebase, and for variables that read from another source, such as the immutable state store or a \textit{prop} parameter from a parent component.
\end{itemize}

Each variable listed below is accompanied by its name, its purpose, the data type it holds one of \textit{String}, \textit{Number}, \textit{Object}, \textit{Date}, \textit{Boolean}, \textit{Function}, or \textit{Array}; the module or function it is used in, and whether it was defined using \textit{let} or \textit{const}.

\subsection{Main Variables} % (fold)
\label{sub:main_variables}
These variables make up the majority used in the system, and are used for a variety of purposes, the extent to which is described for each one.
\begin{longtable}{|l|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Name}} & \multicolumn{1}{c|}{\textbf{Module}} & \multicolumn{1}{c|}{\textbf{Type}} & \multicolumn{1}{c|}{\textbf{Stores}} & \multicolumn{1}{c|}{\textbf{Purpose}} \\ \hline
packet                              & PlayQuizContainer                    & const                              & Object                               & Stores the answer packet.             \\ \hline
questionId                          & PlayQuizContainer                    & const                              & Number                               & The current question ID.              \\ \hline
categoryId                          & PlayQuizContainer                    & const                              & Number                               & The current category ID.              \\ \hline
quizInfo                            & PlayQuizContainer                    & let                                & Object                               & Info on current quiz.                 \\ \hline
housePoints                         & ResultsContainer                     & const                              & Object                               & Total house points earned.            \\ \hline
highestScore                        & ResultsContainer                     & const                              & Number                               & Highest house points won.             \\ \hline
winningHouse                        & ResultsContainer                     & const                              & String                               & The winning house.                    \\ \hline
notifSend                           & CreateQuizContainer                  & const                              & Object                               & Notifications library.                \\ \hline
categoryBody                        & CreateQuizContainer                  & let                                & String                               & Body for custom category.             \\ \hline
currentBody                         & CreateQuizContainer                  & let                                & String                               & Current category body.                \\ \hline
newId                               & CreateQuizContainer                  & let                                & Number                               & Latest question ID.                   \\ \hline
deleteId                            & CreateQuizContainer                  & let                                & Number                               & ID of question to delete.             \\ \hline
deleteIndex                         & CreateQuizContainer                  & let                                & Number                               & Index of question to delete.          \\ \hline
nextQuestionIndex                   & CreateQuizContainer                  & let                                & Number                               & Index of the question.                \\ \hline
nextQuestionId                      & CreateQuizContainer                  & let                                & Number                               & ID of the next question.              \\ \hline
currentlyCorrect                    & CreateQuizContainer                  & const                              & Object                               & Currently correct answer.             \\ \hline
id                                  & CreateQuizContainer                  & const                              & Number                               & ID of question to move to.            \\ \hline
finished                            & CreateQuizContainer                  & const                              & Boolean                              & Whether the quiz is finished.         \\ \hline
quiz                                & CreateQuizContainer                  & const                              & Object                               & Structured quiz for DB.               \\ \hline
value                               & CreateQuizContainer                  & let                                & String                               & Current settings value.               \\ \hline
id                                  & CreateQuizContainer                  & const                              & Number                               & ID of the current question.           \\ \hline
currentQuestion                     & CreateQuizContainer                  & const                              & Object                               & Info on the current question.         \\ \hline
notificationTheme                   & CreateQuizContainer                  & const                              & Object                               & Styling for notifications.            \\ \hline
houses                              & LoginContainer                       & const                              & Array                                & The houses in the school.             \\ \hline
years                               & LoginContainer                       & const                              & Array                                & The years in the school.              \\ \hline
quiz                                & LoginContainer                       & const                              & Object                               & Quiz the user has selected.           \\ \hline
questionSchema                      & Question (model)                     & const                              & Object                               & Defines schema for a question.        \\ \hline
answerSchema                        & Answer (model)                       & const                              & Object                               & Defines schema for an answer.         \\ \hline
quizSchema                          & Quiz (model)                         & const                              & Object                               & Defines schema for a quiz.            \\ \hline
router                              & api/index                            & let                                & Object                               & An HTTP router.                       \\ \hline
quiz                                & api/routes/quizzes                   & let                                & Object                               & Holds the quiz schema.                \\ \hline
store                               & index                                & const                              & Object                               & Access point for immutable state.     \\ \hline
history                             & index                                & const                              & Object                               & Stores browser history.               \\ \hline
socket                              & quizEvents                           & const                              & Object                               & Links module to socket server.        \\ \hline
io                                  & quizSockets                          & let                                & Object                               & Connects socket server to index.      \\ \hline
quizIndex                           & quizSockets                          & let                                & String                               & Address to quiz API.                  \\ \hline
jobs                                & quizSockets                          & let                                & Object                               & Holds the scheduled quiz tasks.       \\ \hline
currentQuiz                         & quizSockets                          & let                                & Object                               & Holds the quiz currently running.     \\ \hline
quizStatus                          & quizSockets                          & let                                & String                               & Current status of the quiz.           \\ \hline
players                             & quizSockets                          & let                                & Array                                & Array of all connected players.       \\ \hline
answers                             & quizSockets                          & let                                & Object                               & Sorted hash of all user's answers.    \\ \hline
housePoints                         & quizSockets                          & let                                & Object                               & Current house points total.           \\ \hline
houses                              & quizSockets                          & const                              & Array                                & The houses in the school.             \\ \hline
quizStart                           & quizSockets                          & const                              & Date                                 & Start date for the next quiz.         \\ \hline
countdownStart                      & quizSockets                          & let                                & Date                                 & Time that countdown wills start.      \\ \hline
totalQuizDuration                   & quizSockets                          & let                                & Number                               & Time in ms of next quiz.              \\ \hline
showResults                         & quizSockets                          & let                                & Date                                 & Time that results be shown.           \\ \hline
quizFinish                          & quizSockets                          & let                                & Date                                 & Time that quiz will finish.           \\ \hline
questionLength                      & quizSockets                          & let                                & Number                               & Length of question, in ms.            \\ \hline
changeQuestion                      & quizSockets                          & const                              & Date                                 & Time that question will change.       \\ \hline
countdown                           & quizSockets                          & const                              & Function                             & SetInterval for question timer.       \\ \hline
defaultQuiz                         & defaultQuiz                          & const                              & Object                               & Default new quiz loaded.              \\ \hline
choice                              & choice                               & const                              & Any                                  & Random item from array.               \\ \hline
colours                             & colourScheme                         & const                              & Object                               & Different house colour schemes.       \\ \hline
ids                                 & nextBiggest                          & const                              & Array                                & Array of question ids.                \\ \hline
sharedConfig                        & config                               & const                              & Object                               & Config shared between dev and pro.    \\ \hline
proConfig                           & config                               & let                                & Object                               & Production configuration.             \\ \hline
devConfig                           & config                               & let                                & Object                               & Development configuration.            \\ \hline
rootReducer                         & reducers/index                       & const                              & Object                               & Combines all the other reducers.      \\ \hline
store                               & configureStore                       & const                              & Object                               & Store composed with middleware.       \\ \hline
nextRootReducer                     & configureStore                       & const                              & Object                               & The other reducers.                   \\ \hline
defaultState                        & userReducer                          & let                                & Object                               & Default house and year for user.      \\ \hline
defaultState                        & quizReducer                          & let                                & Object                               & Initialises the quiz sections.        \\ \hline
categories                          & normaliseQuiz                        & let                                & Array                                & A normalised array of categories.     \\ \hline
questions                           & normaliseQuiz                        & let                                & Array                                & A normalised array of questions.      \\ \hline
answers                             & normaliseQuiz                        & let                                & Array                                & A normalised array of answers.        \\ \hline
initialState                        & answerStatistics                     & const                              & Object                               & Initialises the algorithm state.      \\ \hline
newState                            & answerStatistics                     & const                              & Object                               & New state constructed in process.     \\ \hline
BarChart                            & ResultsChart                         & const                              & Object                               & Charting library.                     \\ \hline
housePoints                         & ResultsChart                         & const                              & Object                               & Stores the house points locally.      \\ \hline
data                                & ResultsChart                         & let                                & Object                               & Formats house points for chart.       \\ \hline
headingView                         & EditableText                         & let                                & Object                               & The type of heading tag.              \\ \hline
editView                            & EditableText                         & const                              & Object                               & Editing view for text.                \\ \hline
innerClass                          & Select                               & let                                & String                               & Class applied inside select.          \\ \hline
outerClass                          & Select                               & let                                & String                               & Class applied outside select.         \\ \hline
categoryId                          & CreateQuiz                           & let                                & Number                               & ID of current category.               \\ \hline
letters                             & CreateQuiz                           & let                                & Array                                & Stores A, B, C and D as guides.       \\ \hline
categoryName                        & CreateQuiz                           & let                                & String                               & Name of the current category.         \\ \hline
categoryLength                      & CreateQuiz                           & let                                & Number                               & \#questions in the current category.  \\ \hline
questionIndex                       & CreateQuiz                           & let                                & Number                               & Index of the current question.        \\ \hline
textColour                          & LoadQuizPanel                        & let                                & Object                               & Colour of the panel's text.           \\ \hline
receivedTime                        & QuestionTimer                        & let                                & Number                               & The time left until the next ping.    \\ \hline
width                               & QuestionTimer                        & let                                & Number                               & Computed width of question timer.     \\ \hline
letters                             & PlayQuiz                             & let                                & Array                                & Stores A, B, C and D as guides.       \\ \hline
quizInfo                            & PlayQuiz                             & let                                & Object                               & Statistics on the current quiz.       \\ \hline
socket                              & PlayQuizActions                      & const                              & Object                               & Connects module to socket server.     \\ \hline
socket                              & LoginActions                         & const                              & Object                               & Connects module to socket server.     \\ \hline
dismissAfter                        & LoginActions                         & let                                & Number                               & Time in ms until notifications go.    \\ \hline
socket                              & CreatorActions                       & const                              & Object                               & Connects module to socket server.     \\ \hline
\caption{Main variables.}
\end{longtable}
% subsection main_variables (end)


\subsection{String Constants} % (fold)
\label{sub:string_constants}
Unlike the previous collection, these variables merely describe the \textit{actions} that are used in the system - every one defines a ``thing'' that will happen, be that requesting a quiz to load, or deleting an answer. They are all stored in a single file, and referred to throughout the system.
% subsection string_constants (end)
\begin{longtable}{|l|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Name}} & \multicolumn{1}{c|}{\textbf{Module}} & \multicolumn{1}{c|}{\textbf{Type}} & \multicolumn{1}{c|}{\textbf{Stores}} & \multicolumn{1}{c|}{\textbf{Purpose}} \\ \hline
CHANGE\_COLOURS                     & actions                    & const                              & String                               & String constant for action.           \\ \hline
CHANGE\_HOUSE                       & actions                    & const                              & String                               & String constant for action.           \\ \hline
CHANGE\_YEAR                        & actions                    & const                              & String                               & String constant for action.           \\ \hline
CHECK\_IF\_QUIZ\_READY              & actions                    & const                              & String                               & String constant for action.           \\ \hline
QUIZ\_IN\_PROGRESS                  & actions                    & const                              & String                               & String constant for action.           \\ \hline
QUIZ\_IS\_SCHEDULED                 & actions                    & const                              & String                               & String constant for action.           \\ \hline
NO\_QUIZ\_READY                     & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_QUIZ                        & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_QUIZ\_SUCCESS               & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_QUIZ\_FAILURE               & actions                    & const                              & String                               & String constant for action.           \\ \hline
REQUEST\_QUIZZES                    & actions                    & const                              & String                               & String constant for action.           \\ \hline
REQUEST\_QUIZZES\_FAILURE           & actions                    & const                              & String                               & String constant for action.           \\ \hline
RECEIVE\_QUIZZES                    & actions                    & const                              & String                               & String constant for action.           \\ \hline
LOAD\_DEFAULT\_QUIZ                 & actions                    & const                              & String                               & String constant for action.           \\ \hline
QUIZ\_IS\_READY                     & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_ID                          & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_TITLE                       & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_START\_DATE                 & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_START\_TIME                 & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_QUESTION\_LENGTH            & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_BREAK\_LENGTH               & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_IS\_FINISHED                & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPDATE\_ALL\_SETTINGS               & actions                    & const                              & String                               & String constant for action.           \\ \hline
ADD\_CATEGORY                       & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_CATEGORY                    & actions                    & const                              & String                               & String constant for action.           \\ \hline
EDIT\_CATEGORY                      & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_ALL\_CATEGORIES             & actions                    & const                              & String                               & String constant for action.           \\ \hline
ADD\_QUESTION                       & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_QUESTION                    & actions                    & const                              & String                               & String constant for action.           \\ \hline
EDIT\_QUESTION                      & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_ALL\_QUESTIONS              & actions                    & const                              & String                               & String constant for action.           \\ \hline
ADD\_ANSWER                         & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_ANSWER                      & actions                    & const                              & String                               & String constant for action.           \\ \hline
EDIT\_ANSWER                        & actions                    & const                              & String                               & String constant for action.           \\ \hline
DELETE\_ALL\_ANSWERS                & actions                    & const                              & String                               & String constant for action.           \\ \hline
UPLOAD\_QUIZ                        & actions                    & const                              & String                               & String constant for action.           \\ \hline
JOIN\_QUIZ                          & actions                    & const                              & String                               & String constant for action.           \\ \hline
BEGIN\_QUIZ                         & actions                    & const                              & String                               & String constant for action.           \\ \hline
SHOW\_RESULTS                       & actions                    & const                              & String                               & String constant for action.           \\ \hline
LEAVE\_QUIZ                         & actions                    & const                              & String                               & String constant for action.           \\ \hline
DECREMENT\_TIME\_LEFT               & actions                    & const                              & String                               & String constant for action.           \\ \hline
SHOW\_NEXT\_QUESTION                & actions                    & const                              & String                               & String constant for action.           \\ \hline
MOVE\_TO\_CATEGORY                  & actions                    & const                              & String                               & String constant for action.           \\ \hline
SELECT\_ANSWER                      & actions                    & const                              & String                               & String constant for action.           \\ \hline
RECEIVE\_ANSWER                     & actions                    & const                              & String                               & String constant for action.           \\ \hline
RECEIVE\_HOUSE\_POINTS              & actions                    & const                              & String                               & String constant for action.           \\ \hline
\caption{String constant variables.}
\end{longtable}
