\subsection{Scoring}
Much of the application will focus on scoring the quiz, using the answer packets that each answer to a question emits.

\subsubsection{Calculate House Points}
This function will calculate the number of house points that an answer packet generates, and then compute an up to date list of the current score for either each year or house.
\begin{verbatim}
process housePoints(packet, correct, keys, prop, state = {}) {
  if state is empty {
    loop through each key
    set state[key] = 0
  }

  if answer is correct and peek is false {
    set score = 1
  } else if answer is correct and peek is true {
    set score = 0.5
  } else set score = 0

  return clone of state
  set packet[prop] to state[packet[prop]] add score
}
\end{verbatim}
By taking a property value as an argument, the function can be used to calculate house points for any specified group, making it more versatile. Additionally, by only computing the most recent state for a single answer packet, and using the previous state as a starting point, it becomes easier to apply the function in the real time scenario it will be used in - an average of 22,500 calls per quiz, many happening at once.

\subsubsection{Highest Value in Object}
This function will calculate the highest value in a given object. It will be used in the most common answer function, displayed below.
\begin{verbatim}
process highest(object) {
  set variable keys to array of object keys

  set variable vals to map over object using
  keys variable for an array of object values

  call max function from standard library on variable vals
  to get the highest value
}
\end{verbatim}

\subsubsection{Correct Answer}
Using an answer packet, returns true if the user chose the correct answer.
\begin{verbatim}
process isCorrect(packet, correctAnswer) {
  if packet.answer = correctAnswer then
    highlight box green.
  else highlight box red.
}
\end{verbatim}

\subsubsection{Maximum Keys}
This function will take an object where every key is a number. It will return the key of the highest number.
\begin{verbatim}
process maxKey(object) {
  perform reduce on object ->
  if obj[a] > obj[b] then return a
  else return b
}
\end{verbatim}

\subsubsection{Most Common Answer}
Using the answere packet, this function will work out the most common answers for each question at any one point in the quiz. It works in much the same way as the function for calculating house points, but the appending operations differ so a new function is needed.
\begin{verbatim}
process commonAnswer(packet, keys, state) {
  set variable innerTree to object containing keys: {
    mode: undefined,
    array with houses: 0
  }

  if the state is empty, set state to innerTree

  set newState to a clone of state, but set the answer
  frequency for the house the user chose to itself + 1

  set the mode property on newState to the largest
  value out of the house frequencies

  return newState
}
\end{verbatim}
