\subsection{API Routes} % (fold)
\label{sub:api_routes}
This subsection lists the RESTful API routes - the section of the program that manages the database.
\input{./tex/program_documentation/listings/server/api_routes.tex}
% subsection api_routes (end)

\subsection{API Models} % (fold)
\label{sub:api_models}
This subsection lists the RESTful API resource models, defining exactly what a quiz, form, etc. look like.
\input{./tex/program_documentation/listings/server/api_models.tex}
% subsection api_models (end)

\subsection{Utility Functions} % (fold)
\label{sub:utility_functions}
This subsection lists the utility functions used through the system. These functions, often used multiple times in different places, are used to extract out common functionality into its own module.
\input{./tex/program_documentation/listings/utils.tex}
% subsection utility_functions (end)

\subsection{Library Functions} % (fold)
\label{sub:library_functions}
This subsection lists the more advanced functions that are used. Focusing on aspects like scoring, these algorithms form the backbone of the processing that takes place for the quiz.
\input{./tex/program_documentation/listings/libs.tex}
% subsection library_functions (end)

\subsection{Action Creators} % (fold)
\label{sub:action_creators}
This subsection lists the action creators. These either construct an object that can be consumed by the reducers, or dispatch actions with side-effects, such as calling the API, which in turn affects an element in state.
\input{./tex/program_documentation/listings/actions.tex}
% subsection action_creators (end)

\subsection{Reducers} % (fold)
\label{sub:reducers}
This subsections lists the application's state reducers.
\input{./tex/program_documentation/listings/reducers.tex}
% subsection reducers (end)

\subsection{Sockets} % (fold)
\label{sub:sockets}
This subsection lists the socket controllers used in the application. In order to allow the different clients (players) to communicate with one another, a concept known as web sockets is utilised. Web sockets allow a continual, bi-directional connection to be set up between each client and the server, facilitating the broadcasting and receiving of messages. In this manner, all of the multiplayer components to the quiz are controlled through these files.
\input{./tex/program_documentation/listings/sockets.tex}
% subsection sockets (end)

\subsection{Components} % (fold)
\label{sub:reducers}
This subsections lists the application's components. Components make up the vast majority of the codebase, as they combine both markup - a description of what should be shown - and logic. The first three components are more advanced, as they interact directly with the applications's state. Other components are less intelligent, and rely on properties passed down from the more advanced components to perform actions and read data.
\input{./tex/program_documentation/listings/components.tex}
% subsection reducers (end)

\subsection{Application Tooling} % (fold)
\label{sub:api_models}
This subsection lists the tooling and build process that is required for the application to run. Though not technically part of the source, a strong understanding is vital if one is to come to terms with the project.
\input{./tex/program_documentation/listings/tooling.tex}
% subsection api_models (end)

\subsection{Styles} % (fold)
\label{sub:styles}
This subsection lists the stylesheets that control the majority of the application's visual aspects.
\input{./tex/program_documentation/listings/styles.tex}
% subsection styles (end)
