\subsection{Quiz Creator Test Plan}
This sub section outlines the data that will be used to test the functionality of the quiz creator.

\subsubsection{Add Question}
\begin{itemize}
\item Press the add question button to create question 02.
\end{itemize}
\textbf{Expected result}: new question should be added.

\subsubsection{Edit Question}
\begin{itemize}
\item Click question title
\item Type in "Who is the Prime Minister?"
\end{itemize}
\textbf{Expected result}: question title should be "Who is the Prime Minister?"

\subsubsection{Delete Question}
\begin{itemize}
\item Press the add question button to create question 02.
\item Press the delete question button to delete question 02.
\end{itemize}
\textbf{Expected result}: question 02 should be deleted.

\subsubsection{Add Category}
\begin{itemize}
\item Press the add category button, and call it "Literature".
\end{itemize}
\textbf{Expected result}: new category "Literature" should be created, with a default question ready.

\subsubsection{Delete Category}
\begin{itemize}
\item Press the add category button, and call it "Literature".
\item Press the delete category button
\end{itemize}
\textbf{Expected result}: category "Literature" should be deleted along with all questions inside.

\subsubsection{Rename Category}
\begin{itemize}
\item Press the add category button, and call it "Literature".
\item Press the rename category button and type in "History".
\end{itemize}
\textbf{Expected result}: category "Literature" should be renamed to "History".

\subsubsection{Mark Answer as Correct}
\begin{itemize}
\item Press the second check mark on Answer 2.
\end{itemize}
\textbf{Expected result}: answer 3 should no longer be marked as correct; answer 2 should be.

\subsubsection{Edit Answer}
\begin{itemize}
\item Click answer 01
\item Type in "Who is the Prime Minister?"
\end{itemize}
\textbf{Expected result}: answer body should be "Who is the Prime Minister?"

\subsubsection{Save Quiz}
\begin{itemize}
\item Create the following quiz:
\begin{Verbatim}[fontsize=\small]
{
  title: 'Summer Term House Quiz',
  start: new Date(),
  questionIntervals: 10000,
  realtimeGraphics: true,
  intervalLength: 300000,
  categories: [
    {
      name: 'History',
      questions: [
        {
          title: 'Who killed JFK?',
          answers: [
            { text: 'Bill Osmond', correct: false },
            { text: 'Lee Harvey Oswald', correct: true },
            { text: 'Henry Kissinger', correct: false }
          ]
        },
        {
          title: 'Who was the British Prime Minister in 1916?',
          answers: [
            { text: 'David Lloyd George', correct: true },
            { text: 'Lee Harvey Oswald', correct: false },
            { text: 'Lord Liverpool', correct: false }
          ]
        }
      ]
    },
    {
      name: 'Sport',
      questions: [
        {
          title: 'Who won the 1966 world cup?',
          answers: [
            { text: 'England', correct: true },
            { text: 'Wales', correct: false },
            { text: 'Scotland', correct: false },
            { text: 'Uzbekistan', correct: false }
          ]
        },
        {
          title: 'Which city hosted the 1924 Summer Olympics?',
          answers: [
            { text: 'Brussels', correct: false },
            { text: 'Orelans', correct: false },
            { text: 'Madrid', correct: false },
            { text: 'Paris', correct: true }
          ]
        }
      ]
    },
    {
      name: 'Literature',
      questions: [
        {
          title: 'Who serves as the main character in "Crime and Punishment"?',
          answers: [
            { text: 'Raskolnikov', correct: true },
            { text: 'Razumikhin', correct: false },
            { text: 'Porifry Petrovich', correct: false },
            { text: 'Svidrigailov', correct: false }
          ]
        },
        {
          title: 'Which literary genre does "Ulysses" belong to?',
          answers: [
            { text: 'Modernist', correct: true },
            { text: 'Post-modernist', correct: false },
            { text: 'Romance', correct: false },
            { text: 'Thriller', correct: false }
          ]
        }
      ]
    }
  ]
}
\end{Verbatim}

\item Press the save quiz button.
\end{itemize}
\textbf{Expected result}: quiz should be saved to database and green success notification should appear.
