\subsection{Login Screen Testing} % (fold)
\label{sub:login_screen_testing}
This subsection shows the test data that will be used to test the login screen. It should be noted that the login screen serves as a ``portal'' to other aspects of the system, displaying a number of different options based on context. The test data below will include full details of how such contextual situations should be replicated.
% subsection login_screen_testing (end)

\subsubsection{Connect to State Store} % (fold)
\label{ssub:connect_to_state_store}
\begin{enumerate}[leftmargin=*]
\item Open the developer tools, navigate to LoginContainer, and check that the store has been passed in the props list.\\\\
\textit{Expected result}: Connection to state store should be open.
\end{enumerate}
% subsubsection connect_to_state_store (end)

\subsubsection{Colours} % (fold)
\label{ssub:colours}
This section demonstrates how to test that the system is properly able to theme itself depending on the colour's selected.
\begin{enumerate}
\item Select ``Acton'' in the house box.\\\\
\textit{Expected result}: Interface should turn blue.\\

\item Select ``Baxter'' in the house box.\\\\
\textit{Expected result}: Interface should turn orange.\\

\item Select ``Clive'' in the house box.\\\\
\textit{Expected result}: Interface should turn green.\\

\item Select ``Darwin'' in the house box.\\\\
\textit{Expected result}: Interface should turn purple.\\

\item Select ``Houseman'' in the house box.\\\\
\textit{Expected result}: Interface should turn red.\\

\item Select ``Webb'' in the house box.\\\\
\textit{Expected result}: Interface should turn yellow.
\end{enumerate}
% subsubsection colours (end)

\subsubsection{Load Quizzes} % (fold)
\label{ssub:load_quizzes}
\begin{enumerate}[leftmargin=*]
\item Create and save a quiz with the title ``Testing Quiz''. (\textit{Typical})\\\\
\textit{Expected result}: One quiz with the title ``Testing Quiz'' should be shown in box.\\

\item Create and save five quizzes with the title ``Testing Quiz''. (\textit{Extreme})\\\\
\textit{Expected result}: Five quizzes with the title ``Testing Quiz'' should be shown in box.\\

\item Turn off the internet and press the load quiz button. (\textit{Erroneous})\\\\
\textit{Expected result}: Box should contain message ``Quizzes couldn't be loaded''.\\

\item Do not save any quizzes. (\textit{Null})\\\\
\textit{Expected result}: Box should contain message ``No quizzes available''.
\end{enumerate}
% subsubsection load_quizzes (end)

\subsubsection{Delete Quizzes} % (fold)
\label{ssub:delete_quizzes}
\begin{enumerate}[leftmargin=*]
\item Create and save a quiz with the title ``Testing Quiz''. (\textit{Typical})
\item Press the delete quiz button.\\\\
\textit{Expected result}: Quiz should be removed from the list, and should no longer be in database.
\end{enumerate}
% subsubsection delete_quizzes (end)

\subsubsection{Show Correct Menu Buttons} % (fold)
\label{ssub:give_appropriate_access_to_quiz}
\begin{enumerate}[leftmargin=*]
\item Schedule a quiz for 20 minutes time. (\textit{Typical})\\\\
\textit{Expected result}: Join quiz button should be shown.\\

\item Schedule a quiz for 2 minutes time. (\textit{Typical})\\\\
\textit{Expected result}: Join quiz button should be shown.\\

\item Schedule a quiz for 1 months time. (\textit{Typical})\\\\
\textit{Expected result}: Create and load quiz buttons should be shown.\\

\item Do not schedule any quizzes. (\textit{Null})\\\\
\textit{Expected result}: Create and load quiz buttons should be shown.
\end{enumerate}
% subsubsection give_appropriate_access_to_quiz (end)
