\subsection{Play Quiz Testing} % (fold)
\label{sub:play_quiz_testing}
This subsection demonstrates the test data that should be used to test the main quiz playing interface, as well as the steps that should be performed.

\subsubsection{Connect to State Store} % (fold)
\label{ssub:connect_to_state_store}
\begin{enumerate}[leftmargin=*]
\item Open the developer tools, navigate to PlayQuizContainer, and check that the store has been passed in the props list.\\\\
\textit{Expected result}: Connection to state store should be open.
\end{enumerate}
% subsubsection connect_to_state_store (end)

\subsubsection{Move Questions on Time} % (fold)
\label{ssub:move_questions_on_time}
\begin{enumerate}[leftmargin=*]
\item Create and save a quiz with the title ``Testing Quiz'', and the following questions:
\begin{enumerate}
\item Who is the French Premier?
\item Who won the 1960 World Cup?
\item What is the capital of Iceland?
\end{enumerate}
Set it for two minutes time, and join the quiz.
\item When the quiz is in progress, the questions should navigate automatically in this order:
\begin{enumerate}
\item 0-10 seconds - \textit{Who is the French Premier?}
\item 10-20 seconds - \textit{Who won the 1960 World Cup?}
\item 20-30 seconds - \textit{What is the capital of Iceland?}
\end{enumerate}
\end{enumerate}
% subsubsection move_questions_on_time (end)
% subsection play_quiz_testing (end)

\subsubsection{End Quiz at Correct Time} % (fold)
\label{ssub:end_quiz_at_correct_time}
\begin{enumerate}[leftmargin=*]
\item Create and save a quiz with the title ``Testing Quiz'', and the single default question. Set it for two minutes time, and join the quiz.
\item After 15 seconds, the quiz should end, and the login page should be shown, displaying the create and load quiz buttons should be shown.
\end{enumerate}
% subsubsection end_quiz_at_correct_time (end)