\subsection{Validation Test Plan} % (fold)
\label{sub:validation_testing}
This subsection displays the test data that will be used to test the validation used throughout the system, and the responses that should occur when the data is entered.

\subsubsection{Only Integers in Question and Break Fields} % (fold)
\label{ssub:only_numbers_in_question_and_break_fields}
This validation will ensure that the question and break fields only accept integers, as they are used in the scheduling of the quiz and so must be validated.
\begin{enumerate}[leftmargin=*]
  \item Enter ``10'' into the question length and break fields. (\textit{Typical})\\\\
  \textit{Expected result}: Nothing should happen, as the data is as expected.\\

  \item Attempt to enter ``abc'' into the question length and break fields. (\textit{Extreme})\\\\
  \textit{Expected result}: The fields should prevent such characters being inserted.\\

  \item Do not enter anything into the fields and save. (\textit{Null})\\\\
  \textit{Expected result}: Nothing should change, as the previous values will not have been updated.\\
\end{enumerate}
% subsubsection only_numbers_in_question_and_break_fields (end)

\subsubsection{Minimum Question Length} % (fold)
\label{ssub:minimum_question_length}
Students should be given a minimum of five seconds to answer a question. This validation ensures that this value is enforced when setting a custom question length.
\begin{enumerate}[leftmargin=*]
  \item Enter ``10'' into the question length field. (\textit{Typical})\\\\
  \textit{Expected result}: Nothing should happen, as the data is as expected.\\

  \item Enter ``3'' into the question length field. (\textit{Extreme})\\\\
  \textit{Expected result}: A message should appear, stating that questions must be at least 5 seconds.\\

  \item Enter ``-8238'' into the question length field. (\textit{Erroneous})\\\\
  \textit{Expected result}: A message should appear, stating that questions must be at least 5 seconds.
\end{enumerate}
% subsubsection minimum_question_length (end)

\subsubsection{Minimum Break Length} % (fold)
\label{ssub:minimum_question_length}
Students should be given a minimum of one minute in a break. This validation ensures that this value is enforced when setting a custom break length.
\begin{enumerate}[leftmargin=*]
  \item Enter ``5'' into the break length field. (\textit{Typical})\\\\
  \textit{Expected result}: Nothing should happen, as the data is as expected.\\

  \item Enter ``0.5'' into the break length field. (\textit{Extreme})\\\\
  \textit{Expected result}: A message should appear, stating that breaks must be at least 1 minute.\\

  \item Enter ``-8238'' into the break length field. (\textit{Erroneous})\\\\
  \textit{Expected result}: A message should appear, stating that breaks must be at least 1 minute.
\end{enumerate}

\subsubsection{One Correct Answer Per Question} % (fold)
\label{ssub:one_correct_answer_}
Each question can only have one correct answer. This aspect of the validation will ensure that only one answer per question can be marked as correct in the quiz editor.
\begin{enumerate}[leftmargin=*]
  \item Create a new quiz.
  \item Mark the first answer as correct by clicking on the tick icon.\\\\
  \textit{Expected result}: The tick in the first answer should now be highlighted, and the previous tick should be pale.
\end{enumerate}
% subsubsection one_correct_answer_ (end)

\subsubsection{Question and Answer Fields Not Blank} % (fold)
\label{ssub:quiz_fields_not_blank}
The question and answer fields must always have a value in them so that they can be displayed in the quiz player. This validation ensures that they can never be left blank.

\textit{\textbf{Note:} Both the question and answer fields make use of the same custom input component (see EditableText in the listings), so it is only necessary to test one of them.}

\begin{enumerate}[leftmargin=*]
  \item Create a new quiz.
  \item Click the question title, which by default should be ``I'm the question title - tap to edit me!''.
  \item Type in ``Who is the current Queen of England?''
  \item Use the backspace key to remove the text.
  \item Click out of the question title.\\\\
  \textit{Expected result}: The question title should have returned to ``I'm the question title - tap to edit me!''.
\end{enumerate}
% subsubsection quiz_fields_not_blank (end)
% subsection validation_testing (end)
