\section{Acceptance Testing}
The system was passed to a friend for testing, with the request that he note down sections that he both liked and disliked. He had the following positive comments about the application:

\begin{itemize}
  \item The different colour schemes are effective, and are a useful differentiator between the houses. They also give the program a nice, fun feel, which fits in with the audience.

  \item It's very easy to make a quiz, as all the buttons are clear, with all the functions labelled. I think it would be suitable for someone who isn't very skilled with technology.

  \item I really like the bouncing animation on the login screen.

  \item The timer in the play quiz screen makes it really exciting to play on; there's a lot of tension.
\end{itemize}

He also had the following, less positive, notes:

\begin{itemize}
  \item At first I didn't know how to change the question title. You could make this a bit clearer by adding a box around it, or something.

  \item When there are a lot of people on the quiz, the program slows down quite a lot, and the timer bar is very jittery.

  \item It's a shame that there aren't any live visualisations to see what other people are answering.
\end{itemize}

As can be gleaned from the notes above, the tester's overall opinion of the system was strong, especially in the quiz creator interface. This is not surprising, as a large amount of time was spent making this work properly. The quiz playing interface lacks the same amount of polish, and this was picked up by the tester, though he did comment that it was sufficiently tence and exciting due to the inclusion of the live countdown timer.
