\part{Analysis}
This initial part of the documentation features detailed information on the analysis that was performed on the business. It includes background information pertaining to the business, as well as an in-depth investigation on the current system in place, featuring questionnaires, interviews, and observations. Also included is a problem definition, wherein the broad aims of the project are outlined; this definition also makes reference to the limitations of the solution. Finally, detailed objectives are clearly laid out, providing an overview of exactly what the solution should achieve.

\section{Background}

\subsection{About the Business}
The Priory School is a medium sized secondary school located in Shrewsbury, Shropshire. The school is a founding member of the Salop Teaching Alliance, and employs over 100 teaching staff, with approximately 900 pupils on roll. Pupils range in age from 11 - 16, and each belongs to an individual form group. During it's previous two inspections, Ofsted judged the school to be Outstanding, the highest possible rating. Additionally, the school has the highest attendance rate in the county, and achieves exam results well above the national average. 

A change of leadership in January 2015 resulted in the previous headteacher, Ms Candy Garbett, leaving the school; Mr Michael Barrett, previously of Adams Grammar School, Newport, became the new principal. Following this change in leadership, the path has opened up for new and innovative changes to take place within the school, opening the way for this solution.

\subsection{About the Project}
Like many schools, The Priory School makes use of a form time in the afternoon. During this process, students are registered, bulletins are read out, and a timetabled activity is carried out; these activities usually include silent reading, a group debate, or, on some occasions, quizzes.

\section{Investigation of the Current System}

\subsection{Overview}
\subsection{Interviews}
\subsection{Questionnaires}
\subsection{Observations}
\subsection{Documents}
\subsection{Similar Systems}
\subsection{Justification of Methods}
\subsection{IPSO Chart}
\subsection{Limitations of Current System}

\section{Problem Definition}

\subsection{Broad Aims}

\subsection{Possible Limitations}

\section{Objectives}